Untitled

### 2023-10-27 code/analysis_Redo.Rmd
clustering analysis of incumbents and rivals

>>>>

## Ratio of Distance between incumbent sites and rival
```{r}

mm.dist <-   df.p %>% 
  filter(Year.y == Att.z) %>% 
  filter(ClinicType == "Incumbent") %>% 
  select(Zip, value, ClinicType, long, lat) %>% 
  unique() %>% 
  arrange(Zip)

vec <- 0
for (k in 1:length(unique(mm.dist$Zip))){

 mm.temp <- mm.dist %>% filter(Zip == unique(mm.dist$Zip)[k]) %>% select(long, lat)
 mm.temp <- dist(mm.temp, upper = FALSE)
 vec <- c(vec, mean(mm.temp, na.rm = TRUE))
}

inc.dist <- data.frame(Zip = unique(mm.dist$Zip), DistIncs = vec[-1]* 111.139)

mm.dist <-   df.p %>% 
  filter(Year.y == Att.z) %>% 
  filter(ClinicType == "Rival") %>% 
  select(Zip, value, ClinicType, long, lat) %>% 
  unique() %>% 
  arrange(Zip)

vec <- 0
for (k in 1:length(unique(mm.dist$Zip))){

 mm.temp <- mm.dist %>% filter(Zip == unique(mm.dist$Zip)[k]) %>% select(long, lat)
 mm.temp <- dist(mm.temp, upper = FALSE)
 vec <- c(vec, mean(mm.temp, na.rm = TRUE))
}

rival.dist <- data.frame(Zip = unique(mm.dist$Zip), DistRivals = vec[-1]* 111.139)

df.p %>% 
  filter(Year.y == Att.z) %>% 
  filter(ClinicType == "Incumbent") %>%
  select(Zip, xcoor, ycoor, Radius) %>% 
  full_join(df.p %>% 
  filter(Year.y == Att.z) %>% 
  filter(ClinicType == "Rival") %>%
  select(Zip, xcoor, ycoor), by = c("Zip")) %>% 
  mutate(DistIncumbtoRival = sqrt((xcoor.x - xcoor.y)^2 + (ycoor.x - ycoor.y)^2)) %>% 
  group_by(Zip) %>% 
  summarise(SD = sd(DistIncumbtoRival, na.rm = TRUE), DistIncumbtoRival = mean.nas(DistIncumbtoRival), Radius = mean(Radius)) %>% 
  left_join(inc.dist, by = c("Zip")) %>% 
  left_join(rival.dist, by = c("Zip")) %>% 
  mutate(DistIncs = DistIncs / Radius, DistRivals = ifelse(DistRivals == "NaN", NA, DistRivals / Radius)) %>% 
  select(DistIncumbtoRival, DistIncs, DistRivals) %>% 
  tbl_summary(statistic = list(all_continuous() ~ "{mean} ({sd})"), missing = "no")
  #summarise(mean.nas(DistIncumbtoRival), mean.nas(DistIncs ), mean.nas(DistRivals ))
